---
title: "Lab Exercise#2"
author: "Marivic Amuan BSIT 2-C"
date: "`r Sys.Date()`"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,warning=FALSE}
library(rvest)
library(dplyr)
library(polite)
library(stringr)
library(httr2)
```
SCRAPING 50 PRODUCTS 
```{r,warning=FALSE}
url <- "https://www.amazon.com.au/gp/bestsellers/garden/ref=zg_bs_nav_garden_0"
session <- bow(url,user_agent = "Educational Purposes")


#29 PRODUCTS
session <- session ("https://www.amazon.com.au/gp/bestsellers/garden/ref=zg_bs_nav_garden_0")
products <- session %>%
  html_nodes("div._cDEzb_p13n-sc-css-line-clamp-3_g3dy1") %>%
  html_text()
  
productNames <- products[1:29]
productNames

#20 PRODUCTS
session1.2 <- session ("https://www.amazon.com.au/gp/bestsellers/garden/ref=zg_bs_pg_2_garden?ie=UTF8&pg=2")
products1 <- session1.2 %>%
  html_nodes("div._cDEzb_p13n-sc-css-line-clamp-3_g3dy1") %>%
  html_text()
  
productNames2 <- products1[1:21]
productNames2

productNames1 <- products[[1]]
productNames1


fiftyProd <- bind_cols(fiftyProd = c(productNames, productNames2))
fiftyProd

write.csv(fiftyProd, "FiftyProducts.csv")
read.csv("FiftyProducts.csv")
```
1ST LINK - Debco Premium Potting Mix 10L 
```{r eval=FALSE}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product1 <- data.frame()

for (page in 1:5) {

link1 <- paste0("https://www.amazon.com.au/product-reviews/B087XK9H6S/ref=cm_cr_arp_d_paging_btm_next_", page, "?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=", page)

session1 <- bow(link1, user_agent = "Educational Purpose")

pro1 <- function(selector) {
  scrape(session1) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

Product <- "Debco Premium Potting Mix 10L"
  Title <- pro1("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro1("span.a-profile-name")[1:10]
  Review <- pro1("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro1("span.a-size-base.a-color-secondary.review-Date")[1:10]
  Rating <- pro1("span.a-icon-alt")[1:10]
  Type <- pro1("span.a-size-mini.a-color-state.a-text-bold")[1:10]

product1 <- rbind(product1, data.frame(
  Product = Product,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product1,"first_product.csv")
head(product1)
```
2nd LINK - ThermoPro TP50 Digital Hygrometer Indoor Thermometer Humidity Monitor with Temperature Humidity Gauge
```{r eval=FALSE}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product2 <- data.frame()

for (page in 1:5) {

link1 <- paste0("https://www.amazon.com/product-reviews/B01H1R0K68/ref=cm_cr_arp_d_paging_btm_next_", page, "?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=", page)

session1 <- bow(link1, user_agent = "Educational Purpose")

pro2 <- function(selector) {
  scrape(session1) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

Product <- "ThermoPro TP50 Digital Hygrometer Indoor Thermometer Humidity Monitor with Temperature Humidity Gauge"
  Title <- pro2("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro2("span.a-profile-name")[1:10]
  Review <- pro2("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro2("span.a-size-base.a-color-secondary.review-Date")[1:10]
  Rating <- pro2("span.a-icon-alt")[1:10]
  Type <- pro2("span.a-size-mini.a-color-state.a-text-bold")[1:10]

product2 <- rbind(product2, data.frame(
  Product = Product,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product2,"second_product.csv")
head(product2)
```
3rd LINK - PALONE Electric Fly Swatter 3000V Bug Zapper Racket 
```{r eval=FALSE}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product3 <- data.frame()

for (page in 1:5) {

link1 <- paste0("https://www.amazon.com/product-reviews/B093PLVSTW/ref=cm_cr_arp_d_paging_btm_next_", page, "?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=", page)

session1 <- bow(link1, user_agent = "Educational Purpose")

pro3 <- function(selector) {
  scrape(session1) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

Product <- "PALONE Electric Fly Swatter 3000V Bug Zapper Racket 2 in 1 Fly Swatter with 1200mAh Battery"
  Title <- pro3("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro3("span.a-profile-name")[1:10]
  Review <- pro3("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro3("span.a-size-base.a-color-secondary.review-Date")[1:10]
  Rating <- pro3("span.a-icon-alt")[1:10]
  Type <- pro3("span.a-size-mini.a-color-state.a-text-bold")[1:10]

product3 <- rbind(product3, data.frame(
  Product = Product,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product3,"third_product.csv")
head(product3)
```
4th LINK - Mortein Powergard Cockroach Baits 12 Pack
```{r eval=FALSE}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product4 <- data.frame()

for (page in 1:5) {

link1 <- paste0("https://www.amazon.com.au/product-reviews/B077BNDYLK/ref=acr_dpx_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar")

session1 <- bow(link1, user_agent = "Educational Purpose")

pro4 <- function(selector) {
  scrape(session1) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

Product <- "Mortein Powergard Cockroach Baits 12 Pack"
  Title <- pro4("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro4("span.a-profile-name")[1:10]
  Review <- pro4("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro4("span.a-size-base.a-color-secondary.review-Date")[1:10]
  Rating <- pro4("span.a-icon-alt")[1:10]
  Type <- pro4("span.a-size-mini.a-color-state.a-text-bold")[1:10]

product4 <- rbind(product4, data.frame(
  Product = Product,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product4,"fourth_product.csv")
head(product4)
```
5th LINK - XLUX Soil Moisture Sensor Meter Water Monitor
```{r eval=FALSE}

product5 <- data.frame()

for (page in 1:5) {

link1 <- paste0("https://www.amazon.com/product-reviews/B014MJ8J2U/ref=cm_cr_arp_d_paging_btm_next_", page, "?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=", page)

session1 <- bow(link1, user_agent = "Educational Purpose")

pro5 <- function(selector) {
  scrape(session1) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

Product <- "XLUX Soil Moisture Sensor Meter Water Monitor, Hygrometer for Gardening, Farming,Plants, No Batteries Required, 2 Pack"
  Title <- pro5("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro5("span.a-profile-name")[1:10]
  Review <- pro5("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro5("span.a-size-base.a-color-secondary.review-Date")[1:10]
  Rating <- pro5("span.a-icon-alt")[1:10]
  Type <- pro5("span.a-size-mini.a-color-state.a-text-bold")[1:10]

product5<- rbind(product5, data.frame(
  Product = Product,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product5,"fifth_product.csv")
head(product5)
```
6th LINK - PALONE Electric Bug Zapper 3200V Mosquito Zapper Killer 
```{r eval=FALSE}

product6 <- data.frame()

for (page in 1:5) {

link1 <- paste0("https://www.amazon.com/product-reviews/B0BTRSDTFV/ref=cm_cr_arp_d_paging_btm_next_", page, "?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=", page)

session1 <- bow(link1, user_agent = "Educational Purpose")

pro6 <- function(selector) {
  scrape(session1) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

Product <- "PALONE Electric Bug Zapper 3200V Mosquito Zapper "
  Title <- pro6("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro6("span.a-profile-name")[1:10]
  Review <- pro6("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro6("span.a-size-base.a-color-secondary.review-Date")[1:10]
  Rating <- pro6("span.a-icon-alt")[1:10]
  Type <- pro6("span.a-size-mini.a-color-state.a-text-bold")[1:10]

product6<- rbind(product6, data.frame(
  Product = Product,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product6,"sixth_product.csv")
head(product6)
```
7th LINK - Jabykare Extra Large Outdoor Rug(150x245cm) 
```{r eval=FALSE}
product7 <- data.frame()

for (page in 1:5) {

link1 <- paste0("https://www.amazon.com.au/product-reviews/B0CB5SWYM1/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=", page)

session1 <- bow(link1, user_agent = "Educational Purpose")

pro7 <- function(selector) {
  scrape(session1) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

Product <- "Jabykare Extra Large Outdoor Rug "
  Title <- pro7("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro7("span.a-profile-name")[1:10]
  Review <- pro7("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro7("span.a-size-base.a-color-secondary.review-Date")[1:10]
  Rating <- pro7("span.a-icon-alt")[1:10]
  Type <- pro7("span.a-size-mini.a-color-state.a-text-bold")[1:10]

product7<- rbind(product7, data.frame(
  Product = Product,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product7,"seventh_product.csv")
head(product7)
```
8th LINK - ThermoPro TP49W Hygrometer Indoor Thermometer
```{r}
product8 <- data.frame()

for (page in 1:5) {

link1 <- paste0("https://www.amazon.com.au/product-reviews/B07WCR5Y4B/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session1 <- bow(link1, user_agent = "Educational Purpose")

pro8 <- function(selector) {
  scrape(session1) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

Product <- "ThermoPro TP49W Hygrometer Indoor Thermometer"
  Title <- pro8("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro8("span.a-profile-name")[1:10]
  Review <- pro8("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro8("span.a-size-base.a-color-secondary.review-Date")[1:10]
  Rating <- pro8("span.a-icon-alt")[1:10]
  Type <- pro8("span.a-size-mini.a-color-state.a-text-bold")[1:10]

product8<- rbind(product8, data.frame(
  Product = Product,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product8,"eight_product.csv")
head(product8)
```
9th LINK - Stingmon 12 Pack Sticky Fruit Fly Fungus
```{r}
product9 <- data.frame()

for (page in 1:5) {

link1 <- paste0("https://www.amazon.com.au/product-reviews/B07XLM4FWL/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session1 <- bow(link1, user_agent = "Educational Purpose")

pro9 <- function(selector) {
  scrape(session1) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

Product <- "Stingmon 12 Pack Sticky Fruit Fly Fungus"
  Title <- pro9("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro9("span.a-profile-name")[1:10]
  Review <- pro9("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro9("span.a-size-base.a-color-secondary.review-Date")[1:10]
  Rating <- pro9("span.a-icon-alt")[1:10]
  Type <- pro9("span.a-size-mini.a-color-state.a-text-bold")[1:10]

product9<- rbind(product9, data.frame(
  Product = Product,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product9,"ninth_product.csv")
head(product9)
```
10th LINK - Govee WiFi Thermometer Hygrometer
```{r}
product10 <- data.frame()

for (page in 1:5) {

link1 <- paste0("https://www.amazon.com.au/product-reviews/B09CKZGBC7/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session1 <- bow(link1, user_agent = "Educational Purpose")

pro10 <- function(selector) {
  scrape(session1) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

Product <- "Govee WiFi Thermometer Hygrometer"
  Title <- pro10("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro10("span.a-profile-name")[1:10]
  Review <- pro10("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro10("span.a-size-base.a-color-secondary.review-Date")[1:10]
  Rating <- pro10("span.a-icon-alt")[1:10]
  Type <- pro10("span.a-size-mini.a-color-state.a-text-bold")[1:10]

product10<- rbind(product10, data.frame(
  Product = Product,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product10,"tenth_product.csv")
head(product10)
```
11th LINK - TheFitLife Expandable Garden Hose Pipe 
```{r eval=FALSE}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product11 <- data.frame()

for (page in 1:5) {

link1 <- paste0("https://www.amazon.com.au/product-reviews/B07DCRVJKF/ref=cm_cr_arp_d_paging_btm_next_", page, "?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=", page)

session1 <- bow(link1, user_agent = "Educational Purpose")

pro1 <- function(selector) {
  scrape(session1) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

Product <- "TheFitLife Expandable Garden Hose Pipe - Multi Core Latex and Solid Metal Fittings 8 Pattern Spray Nozzle AU Standard Expanding Kink Free Easy Storage Flexible Water Hose (25FT/7m)"
  Title <- pro11("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro11("span.a-profile-name")[1:10]
  Review <- pro11("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro11("span.a-size-base.a-color-secondary.review-Date")[1:10]
  Rating <- pro11("span.a-icon-alt")[1:10]
  Type <- pro11("span.a-size-mini.a-color-state.a-text-bold")[1:10]

product11 <- rbind(product11, data.frame(
  Product = Product,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product11,"eleventh_product.csv")
head(product11)
```
12th LINK - 40 PCS Sticky Traps
```{r eval=FALSE}
product12 <- data.frame()

for (page in 1:5) {

link12 <- paste0("https://www.amazon.com.au/product-reviews/B09ZXGQZJZ/ref=cm_cr_arp_d_paging_btm_next_", page, "?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=", page)

session12 <- bow(link12, user_agent = "Educational Purpose")

pro12 <- function(selector) {
  scrape(session12) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

Product12 <- "40 PCS Sticky Traps, GeeRic Sticky Fruit Fly and Plant Gnat Bug Traps for Indoor/Outdoor Use, Dual-Sided Blue Sticky Traps Insect Catcher for White Flies, Mosquitos, Fungus Gnats, Flying Insects"
  Title <- pro12("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro12("span.a-profile-name")[1:10]
  Review <- pro12("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro12("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro12("span.a-icon-alt")[1:10]
  Type <- pro12("span.a-size-mini.a-color-state.a-text-bold")[1:10]

product12 <- rbind(product12, data.frame(
  Product = Product12,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product12,"twelfth_product.csv")
head(product12)
```
13th LINK - Mosquito Killer Lamp
```{r eval = FALSE}
product13 <- data.frame()

for (page in 1:5) {
  link13 <- paste0("https://www.amazon.com.au/product-reviews/B0CM35G41R/ref=acr_dpx_hist_1?ie=UTF8&filterByStar=one_star&reviewerType=all_reviews#reviews-filter-bar")
  session13 <- bow(link13, user_agent = "Educational Purpose")

  pro13 <- function(selector) {
    scrape(session13) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  Product13 <- "Mosquito Killer Lamp, Efficient Bug Zapper Electric Fly Zapper, Electric Fly Killer Fly Catcher Fly Traps for Home Use, Insect Killer Fruit Fly Trap Indoor Outdoor for Home"
  Title <- pro13("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro13("span.a-profile-name")[1:10]
  Review <- pro13("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro13("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro13("span.a-icon-alt")[1:10]
  Type <- pro13("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product13 <- rbind(product13, data.frame(
    Product = Product13,
    TitleOfReviews = Title,
    NameOfReviewer = Reviewer,
    Date = Date,
    Ratings = Rating,
    TypeOfReview = Type,
    Reviews = Review
  ))


}

#write in csv
write.csv(product13,"thirteenth_product.csv")
head(product13)
```
14th LINK - Pressure Washer Foam Cannon
```{r eval = FALSE}
product14 <- data.frame()

for (page in 1:5) {

link14 <- paste0("https://www.amazon.com/product-reviews/B09L7RCFH7/ref=acr_dpx_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar")

session14 <- bow(link14, user_agent = "Educational Purpose")

pro14 <- function(selector) {
  scrape(session14) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

Product14 <- "Pressure Washer Foam Cannon, Heavy Duty Foam Wash Gun, Adjustable Car Foam for Pressure Washer with 1/4 Inch Connector, 1 Liter Bottle"
  Title <- pro14("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro14("span.a-profile-name")[1:10]
  Review <- pro14("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro14("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro14("span.a-icon-alt")[1:10]
  Type <- pro14("span.a-size-mini.a-color-state.a-text-bold")[1:10]

product14 <- rbind(product14, data.frame(
  Product = Product14,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product14,"fourteenth_product.csv")
head(product14)
```
15th PRODUCT - Hills Garden Trigger Sprayer, 1 Liter Capacity Multicolor
```{r eval = FALSE}
product15 <- data.frame()

for (page in 1:5) {

link15 <- paste0("https://www.amazon.com.au/product-reviews/B096TVLP81/ref=acr_dpx_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar")

session15 <- bow(link15, user_agent = "Educational Purpose")

pro15 <- function(selector) {
  scrape(session15) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

Product15 <- "Hills Garden Trigger Sprayer, 1 Liter Capacity Multicolor"
  Title <- pro15("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro15("span.a-profile-name")[1:10]
  Review <- pro15("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro15("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro15("span.a-icon-alt")[1:10]
  Type <- pro15("span.a-size-mini.a-color-state.a-text-bold")[1:10]

product15 <- rbind(product15, data.frame(
  Product = Product15,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product15,"fifteenth_product.csv")
head(product15)
```
16th LINK - Indoor Thermometer Hygrometer Humidity Time Monitor Large LCD Display with Alarm Clock
```{r eval = FALSE}
product16 <- data.frame()

for (page in 1:5) {

link16 <- paste0("https://www.amazon.com/product-reviews/B0CB4WR8V9/ref=cm_cr_arp_d_paging_btm_next_", page, "?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=", page)

session16 <- bow(link16, user_agent = "Educational Purpose")

pro16 <- function(selector) {
  scrape(session16) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

Product16 <- "Indoor Thermometer Hygrometer Humidity Time Monitor Large LCD Display with Alarm Clock"
  Title <- pro16("span.a-size-base.review-TitleOfReviews.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro16("span.a-profile-name")[1:10]
  Review <- pro16("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro16("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro16("span.a-icon-alt")[1:10]
  Type <- pro16("span.a-size-mini.a-color-state.a-text-bold")[1:10]

product16 <- rbind(product16, data.frame(
  Product = Product16,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}

#write in csv
write.csv(product16,"sixteenth_product.csv")
head(product16)
```
17th LINK - 50 PCS Sticky Traps
```{r eval = FALSE}
product17 <- data.frame()

for (page in 1:5) {

link17 <- paste0("https://www.amazon.com.au/product-reviews/B0C3GMR48Y/ref=cm_cr_arp_d_paging_btm_next_", page, "?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=", page)

session17 <- bow(link17, user_agent = "Educational Purpose")

pro17 <- function(selector) {
  scrape(session17) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product17 <- "50 PCS Sticky Traps, KIKISML Yellow Dual-Sided Sticky Insect Catcher with Twist Ties Fruit Fly Fungus Gnat Trap Killer for Whiteflies Mosquitos Fungus Aphids Leafminers Indoor Outdoor Use, Yellow"
  Title <- pro17("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro17("span.a-profile-name")[1:10]
  Review <- pro17("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro17("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro17("span.a-icon-alt")[1:10]
  Type <- pro17("span.a-size-mini.a-color-state.a-text-bold")[1:10]

product17 <- rbind(product17, data.frame(
  Product = Product17,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}

#write in csv
write.csv(product17,"seventeenth_product.csv")
head(product17)
```
18th LINK - Raid One Shot Multipurpose Insect Killer
```{r eval = FALSE}
product18 <- data.frame()

for (page in 1:5) {

link18 <- paste0("https://www.amazon.com.au/product-reviews/B09LCCB124/ref=acr_dpx_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar")

session18 <- bow(link18, user_agent = "Educational Purpose")

pro18 <- function(selector) {
  scrape(session18) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

Product18 <- "Raid One Shot Multipurpose Insect Killer, Insect Spray for Flying and Crawling Insects, Odourless, 220g, 1 Count"
  Title <- pro18("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro18("span.a-profile-name")[1:10]
  Review <- pro18("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro18("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro18("span.a-icon-alt")[1:10]
  Type <- pro18("span.a-size-mini.a-color-state.a-text-bold")[1:10]

product18 <- rbind(product18, data.frame(
  Product = Product18,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}

#write in csv
write.csv(product18,"eighteenth_product.csv")
head(product18)
```
19th LINK - Super Ninja Fruit Fly Trap 
```{r eval = FALSE}
product19 <- data.frame()
for (page in 1:5) {

link19 <- paste0("https://www.amazon.com.au/product-reviews/B09SLX6GQS/ref=cm_cr_arp_d_paging_btm_next_", page, "?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=", page)

session19 <- bow(link19, user_agent = "Educational Purpose")

pro19 <- function(selector) {
  scrape(session19) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product19 <- "Super Ninja Fruit Fly Trap - 4 Traps - Highly Effective Ecological Fruit Fly Traps Indoor - Environmentally Responsible Fruit Fly Killer - User Friendly - Up to 3 Weeks per Bottle"
  Title <- pro19("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro19("span.a-profile-name")[1:10]
  Review <- pro19("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro19("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro19("span.a-icon-alt")[1:10]
  Type <- pro19("span.a-size-mini.a-color-state.a-text-bold")[1:10]

product19 <- rbind(product19, data.frame(
  Product = Product19,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}

#write in csv
write.csv(product19,"nineteenth_product.csv")
head(product19)
```
20th LINK - Raid One Shot Crawling Insects Surface Spray Targetkill
```{r eval=FALSE}
product20 <- data.frame()

for (page in 1:5) {
link20 <- paste0("https://www.amazon.com.au/product-reviews/B09H6BMWB8/ref=acr_dpx_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar")

session20 <- bow(link20, user_agent = "Educational Purpose")

pro20 <- function(selector) {
  scrape(session20) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product20 <- "Raid One Shot Crawling Insects Surface Spray Targetkill, Insect Spray with Protective Barrier up to 6 Months, Targeted Nozzle, 300g, 1 Count"
  Title <- pro20("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro20("span.a-profile-name")[1:10]
  Review <- pro20("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro20("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro20("span.a-icon-alt")[1:10]
  Type <- pro20("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  
product20 <- rbind(product20, data.frame(
  Product = Product20,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}

#write in csv
write.csv(product20,"twentieth_product.csv")
head(product20)
```
21st LINK - 304 Stainless Steel Kitchen Cooking Tongs
```{r eval=FALSE}
product21 <- data.frame()
for (page in 1:5) {
link21 <- paste0("https://www.amazon.com/product-reviews/B071RSP6RP/ref=cm_cr_getr_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=", page)

session21 <- bow(link21, user_agent = "Educational Purpose")

pro21 <- function(selector) {
  scrape(session21) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product21 <- "304 Stainless Steel Kitchen Cooking Tongs, 9 and 12 Set of 2 Sturdy Grilling Barbeque Brushed Locking Food Tongs with Ergonomic Grip, Black"
  Title <- pro21("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro21("span.a-profile-name")[1:10]
  Review <- pro21("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro21("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro21("span.a-icon-alt")[1:10]
  Type <- pro21("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product21 <- rbind(product21, data.frame(
  Product = Product21,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}


#write in csv
write.csv(product21,"twentyFirst_product.csv")
head(product21)
```
22th LINK - Debco Perlite for Potting Mixes 5L
```{r}
product22 <- data.frame()
for (page in 1:5) {
link22 <- paste0("https://www.amazon.com.au/product-reviews/B07WQGY1BJ/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=", page)

session22 <- bow(link22, user_agent = "Educational Purpose")

pro22 <- function(selector) {
  scrape(session22) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product22 <- "Debco Perlite for Potting Mixes 5L - Improve Aeration and Moisture Retension - For Creating Own Mixes - Suitable for Propagation or Cutting Mix"
  Title <- pro22("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro22("span.a-profile-name")[1:10]
  Review <- pro22("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro22("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro22("span.a-icon-alt")[1:10]
  Type <- pro22("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product22 <- rbind(product22, data.frame(
  Product = Product22,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}


#write in csv
write.csv(product22,"twentySecond_product.csv")
head(product22)
```
23rd LINK - Fly Fans, Repellent Outdoor Indoor Keep Flies Away
```{r}
product23 <- data.frame()
for (page in 1:5) {
link23 <- paste0("https://www.amazon.com/product-reviews/B0B6R358LV/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session23 <- bow(link23, user_agent = "Educational Purpose")

pro23 <- function(selector) {
  scrape(session23) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product23 <- "Fly Fans, Repellent Outdoor Indoor Keep Flies Away"
  Title <- pro23("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro23("span.a-profile-name")[1:10]
  Review <- pro23("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro23("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro23("span.a-icon-alt")[1:10]
  Type <- pro23("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product23 <- rbind(product23, data.frame(
  Product = Product23,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}


#write in csv
write.csv(product23,"twentyThird_product.csv")
head(product23)
```
24th LINK - AIPER Seagull Pro Cordless Pool Cleaner Robot
```{r}
product24 <- data.frame()
for (page in 1:5) {
link24 <- paste0("https://www.amazon.com.au/product-reviews/B0CDLG8VGJ/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session24 <- bow(link24, user_agent = "Educational Purpose")

pro24 <- function(selector) {
  scrape(session24) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product24 <- "AIPER Seagull Pro Cordless Pool Cleaner Robot"
  Title <- pro24("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro24("span.a-profile-name")[1:10]
  Review <- pro24("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro24("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro24("span.a-icon-alt")[1:10]
  Type <- pro24("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product24 <- rbind(product24, data.frame(
  Product = Product24,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}


#write in csv
write.csv(product24,"twentyFour_product.csv")
head(product24)
```
25th LINK - Garden Hose Expandable
```{r}
product25 <- data.frame()
for (page in 1:5) {
link25 <- paste0("https://amazon.com.au/product-reviews/B09F995DWG/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session25 <- bow(link25, user_agent = "Educational Purpose")

pro25 <- function(selector) {
  scrape(session25) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product25 <- "Garden Hose Expandable"
  Title <- pro25("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro25("span.a-profile-name")[1:10]
  Review <- pro25("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro25("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro25("span.a-icon-alt")[1:10]
  Type <- pro25("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product25 <- rbind(product25, data.frame(
  Product = Product25,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}


#write in csv
write.csv(product25,"twentyFive_product.csv")
head(product25)
```
26th LINK - Premium Stainless Steel Food Tongs
```{r}
product26 <- data.frame()
for (page in 1:5) {
link26 <- paste0("https://www.amazon.com.au/product-reviews/B07G5RRVBC/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session26 <- bow(link26, user_agent = "Educational Purpose")

pro26 <- function(selector) {
  scrape(session26) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product26 <- "Premium Stainless Steel Food Tongs"
  Title <- pro26("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro26("span.a-profile-name")[1:10]
  Review <- pro26("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro26("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro26("span.a-icon-alt")[1:10]
  Type <- pro26("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product26 <- rbind(product26, data.frame(
  Product = Product26,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}


#write in csv
write.csv(product26,"twentySix_product.csv")
head(product26)
```
27th LINK - Indoor Potting Mix
```{r}
product27 <- data.frame()
for (page in 1:5) {
link27 <- paste0("https://www.amazon.com.au/product-reviews/B0B9GSPD9B/ref=acr_dpx_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar")

session27 <- bow(link27, user_agent = "Educational Purpose")

pro27 <- function(selector) {
  scrape(session27) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product27 <- "Indoor Potting Mix"
  Title <- pro27("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro27("span.a-profile-name")[1:10]
  Review <- pro27("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro27("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro27("span.a-icon-alt")[1:10]
  Type <- pro27("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product27 <- rbind(product27, data.frame(
  Product = Product27,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}


#write in csv
write.csv(product27,"twentySeventh_product.csv")
head(product27)
```
28th LINK - Hills 100728 Garden Sprayer
```{r}
product28 <- data.frame()
for (page in 1:5) {
link28 <- paste0("https://www.amazon.com.au/product-reviews/B07WFC5PNQ/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session28 <- bow(link28, user_agent = "Educational Purpose")

pro28 <- function(selector) {
  scrape(session28) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product28 <- "Hills 100728 Garden Sprayer"
  Title <- pro28("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro28("span.a-profile-name")[1:10]
  Review <- pro28("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro28("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro28("span.a-icon-alt")[1:10]
  Type <- pro28("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product28 <- rbind(product28, data.frame(
  Product = Product28,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}


#write in csv
write.csv(product28,"twentyEight_product.csv")
head(product28)
```
29th - TAKRINK Humane Mouse Trap
```{r}
product29 <- data.frame()
for (page in 1:5) {
link29 <- paste0("https://www.amazon.com.au/product-reviews/B09HXDHJG7/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session29 <- bow(link29, user_agent = "Educational Purpose")

pro29 <- function(selector) {
  scrape(session29) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product29 <- "TAKRINK Humane Mouse Trap"
  Title <- pro29("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro29("span.a-profile-name")[1:10]
  Review <- pro29("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro29("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro29("span.a-icon-alt")[1:10]
  Type <- pro29("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product29 <- rbind(product29, data.frame(
  Product = Product29,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}


#write in csv
write.csv(product29,"twentyNinth_product.csv")
head(product29)
```
30th - NA
```{r}

```
31st - Defender Slug and Snail Pellets 600g
```{r}
product31 <- data.frame()
for (page in 1:5) {
link31 <- paste0("https://www.amazon.com.au/product-reviews/B08BXKY7VY/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session31 <- bow(link31, user_agent = "Educational Purpose")

pro31 <- function(selector) {
  scrape(session31) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product31 <- "Defender Slug and Snail Pellets 600g"
  Title <- pro31("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro31("span.a-profile-name")[1:10]
  Review <- pro31("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro31("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro31("span.a-icon-alt")[1:10]
  Type <- pro31("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product31 <- rbind(product31, data.frame(
  Product = Product31,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}


#write in csv
write.csv(product31,"thirtyFirst_product.csv")
head(product31)
```
32nd - Patio Furniture Cover Waterproof Durable Heavy Duty 210D
```{r}
product32 <- data.frame()
for (page in 1:5) {
link32 <- paste0("https://www.amazon.com.au/product-reviews/B09S61TCC8/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session32 <- bow(link32, user_agent = "Educational Purpose")

pro32 <- function(selector) {
  scrape(session32) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product32 <- "Patio Furniture Cover Waterproof Durable Heavy Duty 210D"
  Title <- pro32("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro32("span.a-profile-name")[1:10]
  Review <- pro32("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro32("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro32("span.a-icon-alt")[1:10]
  Type <- pro32("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product32 <- rbind(product32, data.frame(
  Product = Product32,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}


#write in csv
write.csv(product32,"thirtySecond_product.csv")
head(product32)
```
33rd - Weber Q and Family Q with Patio Cart Cover
```{r}
product33 <- data.frame()
for (page in 1:5) {
link33 <- paste0("https://www.amazon.com.au/product-reviews/B0778X7NPB/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session33 <- bow(link33, user_agent = "Educational Purpose")

pro33 <- function(selector) {
  scrape(session33) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product33 <- "Weber Q and Family Q with Patio Cart Cover"
  Title <- pro33("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro33("span.a-profile-name")[1:10]
  Review <- pro33("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro33("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro33("span.a-icon-alt")[1:10]
  Type <- pro33("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product33 <- rbind(product33, data.frame(
  Product = Product33,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}


#write in csv
write.csv(product33,"thirtyThird_product.csv")
head(product33)
```
34th LINK - Hills 100724 Garden Pressure Sprayer, 1 Liter Capacity, Multicolor
```{r}
product34 <- data.frame()
for (page in 1:5) {
link34 <- paste0("https://www.amazon.com.au/product-reviews/B07WFC5PNQ/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session34 <- bow(link34, user_agent = "Educational Purpose")

pro34 <- function(selector) {
  scrape(session34) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product34 <- "Hills 100724 Garden Pressure Sprayer, 1 Liter Capacity, Multicolor"
  Title <- pro34("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro34("span.a-profile-name")[1:10]
  Review <- pro34("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro34("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro34("span.a-icon-alt")[1:10]
  Type <- pro34("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product34 <- rbind(product34, data.frame(
  Product = Product34,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}


#write in csv
write.csv(product34,"thirtyFour_product.csv")
head(product34)
```
35th - LINK - Mortein Fast Knockdown Crawling Insect Killer Odourless 350g
```{r}
product35 <- data.frame()
for (page in 1:5) {
link35 <- paste0("https://www.amazon.com.au/product-reviews/B0768JNL19/ref=acr_dpx_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar")

session35 <- bow(link35, user_agent = "Educational Purpose")

pro35 <- function(selector) {
  scrape(session35) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product35 <- "Mortein Fast Knockdown Crawling Insect Killer Odourless 350g"
  Title <- pro35("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro35("span.a-profile-name")[1:10]
  Review <- pro35("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro35("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro35("span.a-icon-alt")[1:10]
  Type <- pro35("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product35 <- rbind(product35, data.frame(
  Product = Product35,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}


#write in csv
write.csv(product35,"thirtyFifth_product.csv")
head(product35)
```
36th LINK - AISITIN Solar Fountain
```{r}
product36 <- data.frame()
for (page in 1:5) {
  link36 <- paste0("https://www.amazon.com.au/product-reviews/B093FLFT47/ref=cm_cr_getr_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session36 <- bow(link36, user_agent = "Educational Purpose")

pro36 <- function(selector) {
  scrape(session36) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product36 <- "AISITIN Solar Fountain"
  Title <- pro36("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro36("span.a-profile-name")[1:10]
  Review <- pro36("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro36("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro36("span.a-icon-alt")[1:10]
  Type <- pro36("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product36 <- rbind(product36, data.frame(
  Product = Product36,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}


#write in csv
write.csv(product36,"thirtySix_product.csv")
head(product36)
```
37th LINK - Solar Fountain Water Pump Bird Bath
```{r}
product37 <- data.frame()
for (page in 1:5) {
link37 <- paste0("https://www.amazon.com.au/product-reviews/B08CDSZDS7/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session37 <- bow(link37, user_agent = "Educational Purpose")

pro37 <- function(selector) {
  scrape(session37) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product37 <- "Solar Fountain Water Pump Bird Bath"
  Title <- pro37("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro37("span.a-profile-name")[1:10]
  Review <- pro37("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro37("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro37("span.a-icon-alt")[1:10]
  Type <- pro37("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product37 <- rbind(product37, data.frame(
  Product = Product37,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}


#write in csv
write.csv(product37,"thirtySeven_product.csv")
head(product37)
```
38th LINK - Scotts Osmocote Pour and Feed House Plants 500ml
```{r}
product38 <- data.frame()
for (page in 1:5) {
link38 <- paste0("https://www.amazon.com.au/product-reviews/B09CDBCS8Q/ref=acr_dpx_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar")

session38 <- bow(link38, user_agent = "Educational Purpose")

pro38 <- function(selector) {
  scrape(session38) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product38 <- "Scotts Osmocote Pour and Feed House Plants 500ml"
  Title <- pro38("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro38("span.a-profile-name")[1:10]
  Review <- pro38("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro38("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro38("span.a-icon-alt")[1:10]
  Type <- pro38("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product38 <- rbind(product38, data.frame(
  Product = Product38,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}


#write in csv
write.csv(product38,"thirtyEight_product.csv")
head(product38)
```
39th LINK - Miracle-Gro Plant Food Fertiliser, 500G
```{r}
product39 <- data.frame()
for (page in 1:5) {
link39 <- paste0("https://www.amazon.com.au/product-reviews/B003MPIS8Q/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session39 <- bow(link39, user_agent = "Educational Purpose")

pro39 <- function(selector) {
  scrape(session39) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product39 <- "Miracle-Gro Plant Food Fertiliser, 500G"
  Title <- pro39("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro39("span.a-profile-name")[1:10]
  Review <- pro39("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro39("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro39("span.a-icon-alt")[1:10]
  Type <- pro39("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product39 <- rbind(product39, data.frame(
  Product = Product39,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))
}


#write in csv
write.csv(product39,"thirtyNine_product.csv")
head(product39)
```
40th LINK - ThermoPro TP55 Digital Hygrometer Indoor Thermometer
```{r}
product40 <- data.frame()
for (page in 1:5) {
link40 <- paste0("https://www.amazon.com/product-reviews/B06XTPTG1J/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session40 <- bow(link40, user_agent = "Educational Purpose")

pro40 <- function(selector) {
  scrape(session40) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product40 <- "ThermoPro TP55 Digital Hygrometer Indoor Thermometer"
  Title <- pro40("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro40("span.a-profile-name")[1:10]
  Review <- pro40("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro40("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro40("span.a-icon-alt")[1:10]
  Type <- pro40("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product40 <- rbind(product40, data.frame(
  Product = Product40,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product40,"fortieth_product.csv")
head(product40)
```
41st LINK - Scotts Lawn Builder - Premium Slow Release Lawn Fertiliser 2.5kg
```{r}
product41 <- data.frame()
for (page in 1:5) {
link41 <- paste0("https://www.amazon.com.au/product-reviews/B087XGKS61/ref=acr_dpx_hist_5?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews#reviews-filter-bar")

session41 <- bow(link41, user_agent = "Educational Purpose")

pro41 <- function(selector) {
  scrape(session41) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product41 <- "Scotts Lawn Builder - Premium Slow Release Lawn Fertiliser 2.5kg"
  Title <- pro41("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro41("span.a-profile-name")[1:10]
  Review <- pro41("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro41("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro41("span.a-icon-alt")[1:10]
  Type <- pro41("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product41 <- rbind(product41, data.frame(
  Product = Product41,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product41,"fortyFirst_product.csv")
head(product41)
```
42nd LINK - BBdis 2 PCS Naked Gnomes Statues
```{r}
product42 <- data.frame()
for (page in 1:5) {
link42 <- paste0("https://www.amazon.com/product-reviews/B0B5QTK4SX/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session42 <- bow(link42, user_agent = "Educational Purpose")

pro42 <- function(selector) {
  scrape(session42) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product42 <- "BBdis 2 PCS Naked Gnomes Statues"
  Title <- pro42("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro42("span.a-profile-name")[1:10]
  Review <- pro42("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro42("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro42("span.a-icon-alt")[1:10]
  Type <- pro42("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product42 <- rbind(product42, data.frame(
  Product = Product42,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product42,"fortySecond_product.csv")
head(product42)
```
43rd LINK - Bamworld Wood Plant Stand 
```{r}
product43 <- data.frame()
for (page in 1:5) {
link43 <- paste0("https://www.amazon.com/product-reviews/B0BTSQRWH3/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session43 <- bow(link43, user_agent = "Educational Purpose")

pro43 <- function(selector) {
  scrape(session43) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product43 <- "Bamworld Wood Plant Stand"
  Title <- pro43("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro43("span.a-profile-name")[1:10]
  Review <- pro43("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro43("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro43("span.a-icon-alt")[1:10]
  Type <- pro43("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product43 <- rbind(product43, data.frame(
  Product = Product43,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product43,"fortyThird_product.csv")
head(product43)
```
44th LINK - Bosch Home & Garden 18V Cordless Lawn Grass Line Trimmer
```{r}
product44 <- data.frame()
for (page in 1:5) {
link44 <- paste0("https://www.amazon.com.au/product-reviews/B07J3PBL31/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session44 <- bow(link44, user_agent = "Educational Purpose")

pro44 <- function(selector) {
  scrape(session44) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product44 <- "Bosch Home & Garden 18V Cordless Lawn Grass Line Trimmer"
  Title <- pro44("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro44("span.a-profile-name")[1:10]
  Review <- pro44("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro44("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro44("span.a-icon-alt")[1:10]
  Type <- pro44("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product44 <- rbind(product44, data.frame(
  Product = Product44,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product44,"fortyFour_product.csv")
head(product44)
```
45th LINK - AIPER Seagull SE Cordless Pool Cleaner Robot
```{r}
product45 <- data.frame()
for (page in 1:5) {
link45 <- paste0("https://www.amazon.com/product-reviews/B0BCW4MDRX/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session45 <- bow(link45, user_agent = "Educational Purpose")

pro45 <- function(selector) {
  scrape(session45) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product45 <- "AIPER Seagull SE Cordless Pool Cleaner Robot"
  Title <- pro45("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro45("span.a-profile-name")[1:10]
  Review <- pro45("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro45("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro45("span.a-icon-alt")[1:10]
  Type <- pro45("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product45 <- rbind(product45, data.frame(
  Product = Product45,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product45,"fortyFive_product.csv")
head(product45)
```
46th LINK - Bosch Home & Garden Replacment Cutting Line 24m (2.4mm) for AdvancedGrassCut 36 Volt-33
```{r}
product46 <- data.frame()
for (page in 1:5) {
link46 <- paste0("https://www.amazon.com.au/product-reviews/B0BC3GHP1D/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session46 <- bow(link46, user_agent = "Educational Purpose")

pro46 <- function(selector) {
  scrape(session46) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product46 <- "Bosch Home & Garden Replacment Cutting Line 24m (2.4mm) for AdvancedGrassCut 36 Volt-33"
  Title <- pro46("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro46("span.a-profile-name")[1:10]
  Review <- pro46("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro46("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro46("span.a-icon-alt")[1:10]
  Type <- pro46("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product46 <- rbind(product46, data.frame(
  Product = Product46,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product46,"fortySix_product.csv")
head(product46)
```
47th LINK - Bosch Home & Garden Home & Garden 1500 Watt Electric High Pressure Washer Cleaner
```{r}
product47 <- data.frame()
for (page in 1:5) {
link47 <- paste0("https://amazon.com.au/product-reviews/B07J3PBL31/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session47 <- bow(link47, user_agent = "Educational Purpose")

pro47 <- function(selector) {
  scrape(session47) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product47 <- "Bosch Home & Garden Home & Garden 1500 Watt Electric High Pressure Washer Cleaner"
  Title <- pro47("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro47("span.a-profile-name")[1:10]
  Review <- pro47("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro47("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro47("span.a-icon-alt")[1:10]
  Type <- pro47("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product47 <- rbind(product47, data.frame(
  Product = Product47,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product47,"fortySeven_product.csv")
head(product47)
```
48th LINK - ThermoPro TP357 Digital Hygrometer Indoor Thermometer
```{r}
product48 <- data.frame()
for (page in 1:5) {
link48 <- paste0("https://www.amazon.com.au/product-reviews/B08LKCLFR6/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session48 <- bow(link48, user_agent = "Educational Purpose")

pro48 <- function(selector) {
  scrape(session48) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product48 <- "ThermoPro TP357 Digital Hygrometer Indoor Thermometer"
  Title <- pro48("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro48("span.a-profile-name")[1:10]
  Review <- pro48("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro48("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro48("span.a-icon-alt")[1:10]
  Type <- pro48("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product48 <- rbind(product48, data.frame(
  Product = Product48,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product48,"fortyEight_product.csv")
head(product48)
```
49th LINK - Feeke Rat Trap, Large Mouse Traps, Mouse Traps Indoor for Home
```{r}
product49 <- data.frame()
for (page in 1:5) {
link49 <- paste0("https://www.amazon.com.au/product-reviews/B0BBM951HB/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session49 <- bow(link49, user_agent = "Educational Purpose")

pro49 <- function(selector) {
  scrape(session49) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product49 <- "Feeke Rat Trap, Large Mouse Traps, Mouse Traps Indoor for Home"
  Title <- pro49("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro49("span.a-profile-name")[1:10]
  Review <- pro49("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro49("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro49("span.a-icon-alt")[1:10]
  Type <- pro49("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product49 <- rbind(product49, data.frame(
  Product = Product49,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product49,"fortyNine_product.csv")
head(product49)
```
50th LINK - ThermoPro TP65B Digital Wireless Hygrometer Indoor Outdoor
```{r}
product50 <- data.frame()
for (page in 1:5) {
link50 <- paste0("https://www.amazon.com.au/product-reviews/B07C853F81/ref=cm_cr_arp_d_paging_btm_next_", page, "2?ie=UTF8&filterByStar=five_star&reviewerType=all_reviews&pageNumber=2#reviews-filter-bar", page)

session50 <- bow(link50, user_agent = "Educational Purpose")

pro50 <- function(selector) {
  scrape(session50) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
  }

Product50 <- "ThermoPro TP65B Digital Wireless Hygrometer Indoor Outdoor"
  Title <- pro50("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  Reviewer <- pro50("span.a-profile-name")[1:10]
  Review <- pro50("span.a-size-base.review-text.review-text-content")[1:10]
  Date <- pro50("span.a-size-base.a-color-secondary.review-date")[1:10]
  Rating <- pro50("span.a-icon-alt")[1:10]
  Type <- pro50("span.a-size-mini.a-color-state.a-text-bold")[1:10]


product50 <- rbind(product50, data.frame(
  Product = Product50,
  TitleOfReviews = Title,
  NameOfReviewer = Reviewer,
  Date = Date,
  Ratings = Rating,
  TypeOfReview = Type,
  Reviews = Review
))

}

#write in csv
write.csv(product50,"fiftieth_product.csv")
head(product50)
```

```{r}
allproduct<- rbind( product11, product12, product13, product14, product15, product16, product17, product18, product19, product20, product21, product22, product23, product24, product25, product26, product27, product28, product29, product31, product32, product33, product34, product35, product36, product37, product38, product39, product40, product41, product42, product43, product44, product45, product46, product47, product48, product49, product50)

allproduct 

write.csv(allproduct, "AllProduct.csv")
```

