---
title: "Lab Exercise #3"
author: "Marivic Amuan"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
PACKAGES
```{r}
library(rvest)
library(dplyr)
library(polite)
library(stringr)
library(readr)
```
TEN (10) Movie Titles
```{r}
url <- "https://www.imdb.com/chart/top/?ref_=nv_mv_250"

session <- bow(url, user_agent = "Educational Purposes")
imdbMovie <- read_html(url)


#10MOVIES
movieTitle <- imdbMovie %>%
  html_nodes("h3.ipc-title__text") %>%
  html_text()
  
titles <- movieTitle[2:11]
titles
```
First Movie Title URL - "The Shawshank Redemption" 
```{r}
#First Movie Title URL - "The Shawshank Redemption" 
url_1 <- "https://www.imdb.com/title/tt0111161/reviews/?ref_=tt_ql_2"
session <- bow(url_1, user_agent = "Educational Purposes")

movieTitle_1 <- titles[1]
movieTitle_1


#USER NAMES
imdbMovie <- read_html(url_1)

userNames <- imdbMovie %>%
  html_nodes("span.display-name-link") %>%
  html_text()

usersNames_1 <- userNames[1:10]
usersNames_1


#RATINGS
ratings_1 <- imdbMovie %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text()

ratings_1.1 <- ratings_1[1:10]
ratesplit_1 <- unlist(strsplit(ratings_1.1, "\\s+"))
splitrate_1 <- ratesplit_1[c(2,4,6,8,10,12,14,16,18,20)]

print(splitrate_1)


#REVIEW DATE
reviewDate_1 <- imdbMovie %>%
  html_nodes("span.review-date") %>%
  html_text()
  
review_1.1 <- reviewDate_1[1:10]
review_1.1


#TEXT REVIEWS
textReviews_1 <- imdbMovie %>%
  html_nodes("div.text.show-more__control") %>%
  html_text()

textReviews_1 <- textReviews_1[1:10]
splitReviews_1 <- unlist(strsplit(textReviews_1,"\n"))

print(splitReviews_1)


#DATA FRAME (User, Ratings, Review Date, Review)
df <- data_frame(
  MovieTitle = movieTitle_1,
  Usernames = usersNames_1,
  Ratings = splitrate_1,
  ReviewDate= review_1.1,
  Review = splitReviews_1
)


#CSV File
write.csv(df, file = "FirstMovie.csv")
read.csv("FirstMovie.csv")
```
Second Movie - "The GodFather"
```{r}
#Second Movie Title URL - "The GodFather"
url_2 <- "https://www.imdb.com/title/tt0068646/reviews/?ref_=tt_ql_2"
session <- bow(url_2, user_agent = "Educational Purposes")

imdbMovie_2 <- read_html(url_2)

movieTitle_2 <- titles[2]
movieTitle_2


#USER NAMES 
usersNames_2 <- imdbMovie_2 %>%
  html_nodes("span.display-name-link") %>%
  html_text()

usersNames_1.2 <- usersNames_2[1:10]
usersNames_1.2


#RATINGS
ratings_1 <- imdbMovie_2 %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text()

ratings_1.2 <- ratings_1[1:10]
ratesplit_1.2 <- unlist(strsplit(ratings_1.2, "\\s+"))
splitrate_1.2 <- ratesplit_1.2[c(2,4,6,8,10,12,14,16,18,20)]

print(splitrate_1.2)


#REVIEW DATE
reviewDate_2 <- imdbMovie_2 %>%
  html_nodes("span.review-date") %>%
  html_text()
  
reviews_1.2 <- reviewDate_2[1:10]
reviews_1.2


#TEXT REVIEWS
textReviews_1 <- imdbMovie_2 %>%
  html_nodes("div.text.show-more__control") %>%
  html_text()

textReviews_1.1 <- textReviews_1[1:10]
splitReviews_1 <- unlist(strsplit(textReviews_1.1, "\n"))

print(splitReviews_1)


#DATA FRAME (User, Ratings, Review Date, Review)
df <- data_frame(
  MovieTitle = movieTitle_2,
  Usernames = usersNames_1.2,
  Ratings = splitrate_1.2,
  ReviewDate= reviews_1.2,
  Review = splitReviews_1
)



#CSV File
write.csv(df, file = "SecondMovie.csv")
read.csv("SecondMovie.csv")
```
Third Movie - "The Dark Knight"
```{r}
#Third Movie Title URL - "The Dark Knight"
url_3 <- "https://www.imdb.com/title/tt0468569/reviews/?ref_=tt_ql_2"
session <- bow(url_3, user_agent = "Educational Purposes")

imdbMovie_3 <- read_html(url_3)

movieTitle_3 <- titles[[3]]
movieTitle_3

#USERNAMES
usersNames_3 <- imdbMovie_3 %>%
  html_nodes("span.display-name-link") %>%
  html_text()

usersNames1.3 <- usersNames_3[1:10]
usersNames1.3


#RATINGS
rating_1.2 <- imdbMovie_3 %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text()

rating_1.3 <- rating_1.2[1:10]
ratesplit_3 <- unlist(strsplit(rating_1.3, "\\s+"))
splitrate_3 <- ratesplit_3[c(2,4,6,8,10,12,14,16,18,20)]

print(splitrate_3)


#REVIEW DATE
reviewDate_3 <- imdbMovie_3 %>%
  html_nodes("span.review-date") %>%
  html_text()
  
review_1.3 <- reviewDate_3[1:10]
review_1.3


#TEXT REVIEWS
textReviews_3 <- imdbMovie_3 %>%
  html_nodes("div.text.show-more__control") %>%
  html_text()

textReviews_1.3 <- textReviews_3[1:9]
splitReviews_3 <- unlist(strsplit(textReviews_1.3, "\n"))

print(splitReviews_3)


#DATA FRAME (User, Ratings, Review Date, Review)
df <- data.frame(
  MovieTitle = movieTitle_3,
  Usernames = usersNames1.3,
  Ratings = splitrate_3,
  ReviewDate= review_1.3,
  Review = splitReviews_3
)

#THIS IS TO VIEW THE LENGHT OF EACH DATA -- because i have a problem to run my code. I did this with the rest of the codes to recheck the subsets of each datas.

print(length(movieTitle_3))
print(length(usersNames1.3))
print(length(splitrate_3))  
print(length(review_1.3))
print(length(splitReviews_3))  

#CSV File
write.csv(df, file = "ThirdMovie.csv")
read.csv("ThirdMovie.csv")
```
Fourth Movie Title URL - "The GodFather Part II"
```{r}
#Fourth Movie Title URL - "The GodFather Part II"
url_4 <- "https://www.imdb.com/title/tt0071562/reviews/?ref_=tt_ql_2"
session <- bow(url_4, user_agent = "Educational Purposes")

imdbMovie_4 <- read_html(url_4)

movieTitle_4 <- titles[4]
movieTitle_4

#USER NAMES
userNames_4 <- imdbMovie_4 %>%
  html_nodes("span.display-name-link") %>%
  html_text()

usersNames_1.4 <- userNames_4[1:10]
usersNames_1.4


#RATINGS
rating_1.4 <- imdbMovie_4 %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text()

rating_1.4 <- rating_1.4[1:10]
ratesplit_4 <- unlist(strsplit(rating_1.4, "\\s+"))
splitrate_4 <- ratesplit_4[c(2,4,6,8,10,12,14,16,18,20)]

print(splitrate_4)


#REVIEW DATE
reviewDate_4 <- imdbMovie_4 %>%
  html_nodes("span.review-date") %>%
  html_text()
  
review_1.4 <- reviewDate_4[1:10]
review_1.4


#TEXT REVIEWS
textReviews_4 <- imdbMovie_4  %>%
  html_nodes("div.text.show-more__control") %>%
  html_text()

textReviews_1.4 <- textReviews_4[1:8]
splitReviews_1.4 <- unlist(strsplit(textReviews_1.4, "\n"))

print(splitReviews_1.4)



print(length(movieTitle_4))
print(length(usersNames_1.4))
print(length(splitrate_4))  
print(length(review_1.4))
print(length(splitReviews_1.4))

#DATA FRAME (User, Ratings, Review Date, Review)
df <- data.frame(
  MovieTitle = movieTitle_4,
  Usernames = usersNames_1.4,
  Ratings = splitrate_4,
  ReviewDate= review_1.4,
  Review = splitReviews_1.4
)


#CSV File
write.csv(df, file = "FourthMovie.csv")
read.csv("FourthMovie.csv")
```
Fifth Movie Title URL - "12 Angry Men"
```{r}
url_5 <- "https://www.imdb.com/title/tt0050083/reviews/?ref_=tt_ql_2"
session <- bow(url_5, user_agent = "Educational Purposes")

imdbMovie_5 <- read_html(url_5)

movieTitle_5 <- titles[5]
movieTitle_5

#Users
usersNames_5 <- imdbMovie_5 %>%
  html_nodes("span.display-name-link") %>%
  html_text()

usersNames_1.5 <- usersNames_5[1:10]
usersNames_1.5


#RATINGS
rating_5 <- imdbMovie_5 %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text()

rating_1.5 <- rating_5[1:10]
ratesplit_5 <- unlist(strsplit(rating_1.5, "\\s+"))
splitrate_5 <- ratesplit_5[c(2,4,6,8,10,12,14,16,18,20)]

print(splitrate_5)


#REVIEW DATE
reviewDate_5 <- imdbMovie_5 %>%
  html_nodes("span.review-date") %>%
  html_text()
  
review_1.5 <- reviewDate_5[1:10]
review_1.5


#TEXT REVIEWS
textReviews_5 <- imdbMovie_5 %>%
  html_nodes("div.text.show-more__control") %>%
  html_text()

textReviews_1.5 <- textReviews_5[1:10]
splitReviews_5 <- unlist(strsplit(textReviews_1.5, "\n"))

print(splitReviews_5)


#DATA FRAME (User, Ratings, Review Date, Review)
df <- data_frame(
  MovieTitle = movieTitle_5,
  Usernames = usersNames_1.5,
  Ratings = splitrate_5,
  ReviewDate= review_1.5,
  Review = splitReviews_5
)

  
#CSV File
write.csv(df, file = "FifthMovie.csv")
read.csv("FifthMovie.csv")
```
Sixth Movie Title URL - "Schindler's List"
```{r}
#Sixth Movie Title URL - "Schindler's List"
url_6 <- "https://www.imdb.com/title/tt0108052/reviews/?ref_=tt_ql_2"
session <- bow(url_6, user_agent = "Educational Purposes")

imdbMovie_6 <- read_html(url_6)

movieTitle_6 <- titles[6]
movieTitle_6

#USER NAMES 
usersNames_6 <- imdbMovie_6 %>%
  html_nodes("span.display-name-link") %>%
  html_text()

usersNames_1.6 <- usersNames_6[1:10]
usersNames_1.6


#RATINGS
rating_1.6 <- imdbMovie_6 %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text()

rating_1.6 <- rating_1.6[1:10]
ratesplit_6 <- unlist(strsplit(rating_1.6, "\\s+"))
splitrate_6 <- ratesplit_6[c(2,4,6,8,10,12,14,16,18,20)]

print(splitrate_6)


#REVIEW DATE
reviewDate_6 <- imdbMovie_6 %>%
  html_nodes("span.review-date") %>%
  html_text()
  
review_1.6 <- reviewDate_6[1:10]
review_1.6


#TEXT REVIEWS
textReviews_6 <- imdbMovie_6 %>%
  html_nodes("div.text.show-more__control") %>%
  html_text()

textReviews_1.6 <- textReviews_6[1:9]
splitReviews_6 <- unlist(strsplit(textReviews_1.6, "\n"))

print(splitReviews_6)


print(length(movieTitle_6))
print(length(usersNames_1.6))
print(length(splitrate_6))  
print(length(review_1.6))
print(length(splitReviews_6))


#DATA FRAME (User, Ratings, Review Date, Review)
df <- data.frame(
  MovieTitle = movieTitle_6,
  Usernames = usersNames_1.6,
  Ratings = splitrate_6,
  ReviewDate= review_1.6,
  Review = splitReviews_6
)


#CSV File
write.csv(df, file = "SixthMovie.csv")
read.csv("SixthMovie.csv")
```
Seventh Movie Title URL - "The Lord of the Rings: The Return of the King"
```{r}
#Seventh Movie Title URL - "The Lord of the Rings: The Return of the King"
url_7 <- "https://www.imdb.com/title/tt0167260/reviews/?ref_=tt_ql_2"
session <- bow(url_7, user_agent = "Educational Purposes")

imdbMovie_7 <- read_html(url_7)

movieTitle_7 <- titles[7]
movieTitle_7

#USER NAMES
usersNames_7 <- imdbMovie_7 %>%
  html_nodes("span.display-name-link") %>%
  html_text()

usersNames_1.7 <- usersNames_7[1:10]
usersNames_1.7

#RATINGS
rating_1.7 <- imdbMovie_7 %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text()

rating_1.7 <- rating_1.7[1:10]
ratesplit_7 <- unlist(strsplit(rating_1.7, "\\s+"))
splitrate_7 <- ratesplit_7[c(2,4,6,8,10,12,14,16,18,20)]

print(splitrate_7)


#REVIEW DATE
reviewDate_7 <- imdbMovie_7 %>%
  html_nodes("span.review-date") %>%
  html_text()
  
review_1.7 <- reviewDate_7[1:10]
review_1.7


#TEXT REVIEWS
textReviews_7 <- imdbMovie_7 %>%
  html_nodes("div.text.show-more__control") %>%
  html_text()

textReviews_1.7 <- textReviews_7 [1:9]
splitReviews_7 <- unlist(strsplit(textReviews_1.7, "\n"))

print(splitReviews_7)


print(length(movieTitle_7))
print(length(usersNames_1.7))
print(length(splitrate_7))  
print(length(review_1.7))
print(length(splitReviews_7))


#DATA FRAME (User, Ratings, Review Date, Review)
df <- data.frame(
  MovieTitle = movieTitle_7,
  Usernames = usersNames_1.7,
  Ratings = splitrate_7,
  ReviewDate= review_1.7,
  Review = splitReviews_7
)
df

#CSV File
write.csv(df, file = "SeventhMovie.csv")
read.csv("SeventhMovie.csv")
```
Eighth Movie Title URL - "Pulp Fiction"
```{r}
#Eighth Movie Title URL - "Pulp Fiction"
url_8 <- "https://www.imdb.com/title/tt0110912/reviews/?ref_=tt_ql_2"

session <- bow(url_8, user_agent = "Educational Purposes")

imdbMovie_8 <- read_html(url_8)

movieTitle_8 <- titles[8]
movieTitle_8

#USER NAMES
usersNames_8 <- imdbMovie_8 %>%
  html_nodes("span.display-name-link") %>%
  html_text()

usersNames_1.8 <- usersNames_8[1:10]
usersNames_1.8


#RATINGS
rating_1.8 <- imdbMovie_8 %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text()

rating_1.8 <- rating_1.8[1:10]
ratesplit_8 <- unlist(strsplit(rating_1.8, "\\s+"))
splitrate_8 <- ratesplit_8[c(2,4,6,8,10,12,14,16,18,20)]

print(splitrate_8)


#REVIEW DATE
reviewDate_8 <- imdbMovie_8 %>%
  html_nodes("span.review-date") %>%
  html_text()
  
review_1.8 <- reviewDate_8[1:10]
review_1.8


#TEXT REVIEWS
textReviews_8 <- imdbMovie_8 %>%
  html_nodes("div.text.show-more__control") %>%
  html_text()

textReviews_1.8 <- textReviews_8[1:8]
splitReviews_1.8 <- unlist(strsplit(textReviews_1.8, "\n"))

print(splitReviews_1.8)


print(length(movieTitle_8))
print(length(usersNames_1.8))
print(length(splitrate_8))  
print(length(review_1.8))
print(length(splitReviews_1.8))

#DATA FRAME (User, Ratings, Review Date, Review)
df <- data.frame(
  MovieTitle = movieTitle_8,
  Usernames = usersNames_1.8,
  Ratings = splitrate_8,
  ReviewDate= review_1.8,
  Review = splitReviews_1.8
)
df

#CSV File
write.csv(df, file = "EighthMovie.csv")
read.csv("EighthMovie.csv")
```
Ninth Movie Title URL - "The Lord of the Rings: The Fellowship of the Ring"
```{r}
#Ninth Movie Title URL - "The Lord of the Rings: The Fellowship of the Ring"
url_9 <- "https://www.imdb.com/title/tt0120737/reviews/?ref_=tt_ql_2"
session <- bow(url_9, user_agent = "Educational Purposes")

imdbMovie_9 <- read_html(url_9)

movieTitle_9 <- titles[9]
movieTitle_9

#Users
usersNames_9 <- imdbMovie_9 %>%
  html_nodes("span.display-name-link") %>%
  html_text()

usersNames_1.9 <- usersNames_9[1:10]
usersNames_1.9


#RATINGS
rating_1.9 <- imdbMovie_9 %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text()

rating_1.9 <- rating_1.9[1:10]
ratesplit_9 <- unlist(strsplit(rating_1.9, "\\s+"))
splitrate_9 <- ratesplit_9[c(2,4,6,8,10,12,14,16,18,20)]

print(splitrate_9)


#REVIEW DATE
reviewDate_9 <- imdbMovie_9 %>%
  html_nodes("span.review-date") %>%
  html_text()
  
review_1.9 <- reviewDate_9[1:10]
review_1.9


#Text Reviews
textReviews_9 <- imdbMovie_9 %>%
  html_nodes("div.text.show-more__control") %>%
  html_text()

textReviews_1.9 <- textReviews_9[1:7]
splitReviews_9 <- unlist(strsplit(textReviews_1.9, "\n"))

print(splitReviews_9)

print(length(splitReviews_9))


#DATA FRAME (User, Ratings, Review Date, Review)
df <- data.frame(
  MovieTitle = movieTitle_9,
  Usernames = usersNames_1.9,
  Ratings = splitrate_9,
  ReviewDate= review_1.9,
  Review = splitReviews_9
)
df

#CSV File
write.csv(df, file = "NinthMovie.csv")
read.csv("NinthMovie.csv")
```
Tenth Movie Title URL - "Dune: Part Two"
```{r}
#Tenth Movie Title URL - "Dune: Part Two"
url_10 <- "https://www.imdb.com/title/tt15239678/reviews/?ref_=tt_ql_2"
session <- bow(url_10, user_agent = "Educational Purposes")

imdbMovie_10 <- read_html(url_10)

movieTitle_10 <- titles[10]
movieTitle_10


#USER NAMES
usersNames_10 <- imdbMovie_10 %>%
  html_nodes("span.display-name-link") %>%
  html_text()

usersNames_1.10 <- usersNames_10[1:10]
usersNames_1.10


#RATINGS
rating_1.10 <- imdbMovie_10 %>%
  html_nodes("span.rating-other-user-rating") %>%
  html_text()

rating_1.10 <- rating_1.10[1:10]
ratesplit_10 <- unlist(strsplit(rating_1.10, "\\s+"))
splitrate_10 <- ratesplit_10[c(2,4,6,8,10,12,14,16,18,20)]

print(splitrate_10)


#REVIEW DATE
reviewDate_10 <- imdbMovie_10 %>%
  html_nodes("span.review-date") %>%
  html_text()
  
review_1.10 <- reviewDate_10[1:10]
review_1.10


#TEXT REVIEWS
reviews_10 <- imdbMovie_10 %>%
  html_nodes("div.text.show-more__control") %>%
  html_text()

textReviews_1.10 <- reviews_10[1:10]
reviews_10 <- unlist(strsplit(reviews_10, "\n"))

print(textReviews_1.10)
print(length(reviews_10))

  
#DATA FRAME(User, Ratings, Review Date, Review)
df <- data.frame(
  MovieTitle = movieTitle_10,
  Usernames = usersNames_1.10,
  Ratings = splitrate_10,
  ReviewDate= textReviews_1.10,
  Review = reviews_10
)
df

#CSV File

write.csv(df, file = "TenthMovie.csv")
read.csv("TenthMovie.csv")
```

